High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 Experiments.tex
removing a query.
Typos

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead of  scheduling and
bootstraping of AthenaMP instances, the number of events simulated by each
AthenaMP task was reduced to sixteen such that the running time of each
AthenaMP was $\sim 1200$ seconds on average. This experiment design choice
does not affect the objectives or accuracy of the experiments, but allows us
to scale experiments to large node counts by conserving project allocation.

>>>>

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead of  scheduling and
bootstraping of AthenaMP instances, the number of events simulated by each
AthenaMP task was reduced to sixteen such that the running time of each
AthenaMP was \(\approx\)1,200 seconds on average. This experiment design choice
does not affect the objectives or accuracy of the experiments, but allows us
to scale experiments to large node counts by conserving project allocation.
